The Private School Network: Recruiting Visits to Private High Schools by Public and Private Universities

### 2023-11-14 r_r/letter_to_reviewers.Rmd
revising results section

SEEMS TO WANT ADDITIONAL ANALYSES TO ENGAGE W/ RQ3. I'M NOT SURE WHAT TO ADD HERE. COME BACK TO LATER.

>>>>

SEEMS TO WANT ADDITIONAL ANALYSES TO ENGAGE W/ RQ3. I'M NOT SURE WHAT TO ADD HERE. COME BACK TO LATER.
SOLUTION: SAY THAT WE THINK THE AUTHOR IS MAKING A GOOD POINT. INCLUDE THIS POINT AS A LIMITATION. AND AN AREA WHERE FUTURE RESEARCH SHOULD PROBE. SAY THAT IF THE REVIEWER IS DEAD SET ON SOME ADDITIONAL ANALYSES, I WILL MAKE THIS HAPPEN.

POTENTIAL ANALYSIS YOU THOUGHT THROUGH

- WHAT ARE THE CHARACTERISTICS OF PRIVATE SCHOOLS VISITED BY PUBLIC UNIVERSITIES BUT NOT BY PRIVATE UNIVERSITIES 
- REGRESSION ANALYSES; SEPARATE REGRESSION FOR EACH UNIVERSITY

### 2023-11-14 r_r/manuscript_rihe.Rmd
revising results section

Figures \@ref(fig:race-pubu-privhs-pubhs) and \@ref(fig:race-privu-privhs-pubhs) shows the percentage of 12th graders who identify as Black, Latinx, or Native at visited high schools. Consistent with @RN4504, most private high schools enroll relatively few students from historically underrepresented race/ethnicity groups. The top row in the top panel of Figure \@ref(fig:race-pubu-privhs-pubhs) shows that the sum of Black, Latinx, and Native students comprise less than 20% of enrolled students in over over 65%<!--0.6632124--> of schools in private high school universe. At public high schools, Black/Latinx/Native students comprise less than 20% of enrolled students at less than 40% [CRYSTAL CHECK NUMBER] of all public schools.

Figure \@ref(fig:race-pubu-privhs-pubhs) focuses on public universities, showing the racial composition of visited private high schools (top panel) to the racial composition of visited public high schools (bottom panel). START HERE TUESDAY. CONSISTENT WITH DIFFERENCES IN RACIAL COMPOSITION OF THE UNIVERSE OF PUBLIC VS. THE UNIVERSE OF PRIVATE, VISITED PRIVATE SCHOOLS TENDED TO ENROLL A MUCH LOWER SHARE OF BLACK/LATINX THAN VISITED PUBLIC SCHOOLS.

This is reflected in the racial composition of visited schools as well, where the set of visited public high schools generally enroll more Black/Latinx/Native students than the visited private schools for the public research universities in our sample. Unfortunately though, a majority of these public universities tended to visit private high schools at a higher rate than public high schools, as seen earlier in Figure \@ref(fig:actual-proportional-pubu). This disproportionate emphasis on private school visits may shift the racial composition of public universities away from Black/Latinx/Native students.

Therefore, even if universities visited schools with racial composition on par with the universe of private high schools, most visited schools would have relatively few Black/Latinx/Native students enrolled.

Figure \@ref(fig:race-pubu-privu) shows that for most universities in our sample, the set of visited private high schools enrolled *fewer* Black/Latinx/Native students than the universe of private high schools. For public universities, exceptions to this finding were UC-San Diego, UC-Riverside, and -- to a lesser extent -- SUNY Stony Brook. For private universities, Marquette was the only exception to this finding.

@@

Several studies suggest that universities -- particularly elite private universities -- pursue racial diversity by recruiting non-white students who attend predominantly white private high schools [e.g., @RN4495]. Additionally, scholarship that engages with enrollment in private schools by Black students suggests that many high-income Black families began sending their children to elite, predominantly white private schools once these schools were willing to enroll Black students [@RN4724]. Therefore, universities may visit predominantly white private high schools in search of non-white students. One concern about this practice is that non-white students at elite private schools may be in high demand by many universities, but similarly achieving non-white students at predominantly non-white public schools might be ignored.

ADD ADDITIONAL SUBGROUP ANALYSES WITH CRYSTAL...?

- look at racial composition of visited southern schools (public and private)
- look at religious affiliation of visited southern schools?
- look at racial composition of schools visited by some subset of universities?
-

>>>>

Figures \@ref(fig:race-pubu-privhs-pubhs) and \@ref(fig:race-privu-privhs-pubhs) shows the percentage of 12th graders who identify as Black, Latinx, or Native at visited high schools. Consistent with @RN4504, most private high schools enroll relatively few students from historically underrepresented race/ethnicity groups. The top row in the top panel of Figure \@ref(fig:race-pubu-privhs-pubhs) shows that the sum of Black, Latinx, and Native students comprise less than 20% of enrolled students in over over 65%<!--0.6632124--> of schools in private high school universe. At public high schools, Black/Latinx/Native students comprise less than 20% of enrolled students at less than 40% [CRYSTAL CHECK NUMBER] of all public schools. However, most public research universities and all selective private universities visited private high schools at a higher rate than public high schools, as seen earlier in Figures \@ref(fig:actual-proportional-pubu) and \@ref(fig:actual-proportional-privu). Even if universities visited schools with racial composition on par with the universe of private high schools, most visited schools would have relatively few Black/Latinx/Native students enrolled. Therefore, a disproportionate emphasis on visits to public schools may shift the racial composition of public universities away from Black/Latinx/Native students.

@@

Figure \@ref(fig:race-pubu-privhs-pubhs) focuses on public universities, showing the racial composition of visited private high schools (top panel) to the racial composition of visited public high schools (bottom panel). For all public universities, the racial composition of visited public schools contain a much higher share of Black/Latinx/Native students than the racial composition of visited private schools. Figure \@ref(fig:race-pubu-privhs-pubhs) shows that for most universities in our sample, the set of visited private high schools enrolled *fewer* Black/Latinx/Native students than the universe of private high schools. For public universities, exceptions to this finding were UC-San Diego, UC-Riverside, and -- to a lesser extent -- SUNY Stony Brook.

Figure \@ref(fig:race-privu-privhs-pubhs) focuses on selective private universities, showing the racial composition of visited private high schools (top panel) to the racial composition of visited public high schools (bottom panel). Results are very similar to those of public universities. Visited private schools enrolled a much lower share of Black/Latinx/Native students than visited public schools. For Emory, Northwestern, Tufts, Tulane, Case Western Reserve, and University of Denver, at least 75% of visited private schools enrolled less than 20% Black/Latinx/Native students.

Several studies suggest that universities -- particularly elite private universities -- pursue racial diversity by recruiting non-white students who attend predominantly white private high schools [e.g., @RN4495]. Additionally, scholarship that engages with enrollment in private schools by Black students suggests that many high-income Black families began sending their children to elite, predominantly white private schools once these schools were willing to enroll Black students [@RN4724]. Therefore, universities may visit predominantly white private high schools in search of non-white students. One concern about this practice is that non-white students at elite private schools may be in high demand by many universities, but similarly achieving non-white students at predominantly non-white public schools might be ignored [THIS PARAGRAPH SHOULD PROBABLY GO TO DISCUSSION].

ADDITIONAL SUBGROUP ANALYSES

- racial composition of visited southern schools (separat figures for public universities and private universities; top panel is visited private schools; bottom panel is visited public schools; universe is southern schools)

- look at religious affiliation of visited southern schools?
- look at racial composition of schools visited by some subset of universities?
-
